---
title: "Assignment3_Bootstrap_10252018"
author: "Nina Dyatchenko"
date: "October 25, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read this chapter on functions and if/else statements in R:
http://r4ds.had.co.nz/functions.html
Create a markdown report where you execute the code from this chapter, and attempt the exercises after each section. Some of them will be more challenging than others, but I still want you to try to solve them.

Please upload this report to your GitHub by 11:59PM on Sunday, 28 October.

#1 Prerequisites#
Copies of the same code:
```{r}
# tibble builds a simple list/data_frame of a, b, c, and d with 10 values from a normal distribution:
df<- tibble::tibble(
  a=rnorm(10),
  b=rnorm(10),
  c=rnorm(10),
  d=rnorm(10)
)
df

df$a
df$b
df$c
df$d


# rescaling from 0 to 1:
df$a <- (df$a - min(df$a, na.rm = TRUE)) / 
  (max(df$a, na.rm = TRUE) - min(df$a, na.rm = TRUE))
df$b <- (df$b - min(df$b, na.rm = TRUE)) / 
  (max(df$b, na.rm = TRUE) - min(df$b, na.rm = TRUE)) 
df$c <- (df$c - min(df$c, na.rm = TRUE)) / 
  (max(df$c, na.rm = TRUE) - min(df$c, na.rm = TRUE))
df$d <- (df$d - min(df$d, na.rm = TRUE)) / 
  (max(df$d, na.rm = TRUE) - min(df$d, na.rm = TRUE))

df$a
df$b
df$c
df$d
```
Analysing the code: there is one input df$a (or df$b or df$c or df$d).
Rewriting code using a general variable name x:
```{r}
x<- df$a
(x-min(x, na.rm=TRUE))/ (max(x, na.rm=TRUE) - min(x, na.rm=TRUE))
```
Symplify:
```{r}
rng<- range(x, na.rm=TRUE)
x<- (x-rng[1])/ (rng[2]-rng[1])
x
```
Combine all into a function:
```{r}
rescale01<- function(x){
  rng<-range(x, na.rm=T)
  (x-rng[1])/(rng[2]-rng[1])
}
rescale01(c(0, 5, 10))
```
Cheching function with different outputs:
```{r}
rescale01(c(8, 10, -9, 500))
rescale01(c(1, 9, NA, -9))
```
Applying the new function:
```{r}
df$a<- rescale01(df$a)
df$b<- rescale01(df$b)
df$c<- rescale01(df$c)
df$d<- rescale01(df$d)
df$a
```
Adjastign our function to unclude infinitine vlaues:
```{r}
x<- c(1:10, Inf)
rescale01(x)

rescale01<- function(x){
  rng<- range(x, na.rm=T, finite=T)
  (x-rng[1])/(rng[2]-rng[1])
}
rescale01(x)
```

#2 Practice#
###1. Why is TRUE not a parameter to rescale01()? 
The TRUE is an argument of the parameter x. An argument specifies the parameter.

What would happen if x contained a single missing value, and na.rm was FALSE?
All values show as NA. na.rm=F means "do not omit" NA values.
```{r}
x<- c(1:10, NA)
rescale01(x)

rescale01<- function(x){
  rng<- range(x, na.rm=F)
  (x-rng[1])/(rng[2]-rng[1])
}
rescale01(x)
```
###2. In the second variant of rescale01(), infinite values are left unchanged. Rewrite rescale01() so that -Inf is mapped to 0, and Inf is mapped to 1.
```{r}
y<- c(1:10, -Inf)

rescale01<- function(y){
  rng<- range(y, na.rm=T, finite=F)
  (y-rng[1])/(rng[2]-rng[1])
}
rescale01(y)
```
###3. Practice turning the following code snippets into functions. Think about what each function does. 
What would you call it? 
How many arguments does it need? 
Can you rewrite it to be more expressive or less duplicative?

```{r}
z<- c(1:10, NA)

mean(is.na(z)) # shows probability of NA values in a sample

z/ sum(z, na.rm = T) # Gives NA's should not be omited

CV<- sd(z, na.rm = T)/ mean(z, na.rm=T) # coeff. of variation is sd/mean

```
###4. 

data<- read.csv("data/seed_root_herbivores.csv") # Error in file(file, "rt") : cannot open the connection

mean(data$Height)
var(data$Hight)
length(data$Hight)

Standard Error:
sqrt(var(data$Hight)/lenght(data$Hight))
sqrt(var(data$Weight)/length(data$Weight))


###5. Write both_na(), a function that takes two vectors of the same length and returns the number of positions that have an NA in both vectors.

```{r}
#a<- c(NA, 1:10, NA)
b<- c(NA, 3:13, NA)
#(is.na(a))

both_na<- function(a, b){
  frequesncy(is.na(a)-is.na(b))
}
#both_na(a, b)  

```
###6. What do the following functions do? Why are they useful even though they are so short?
```{r}
#is_directory<- function (x) file.info(x)$isdir
#is_readable <- function(x) file.access(x, 4) ==0
#is_directory(x)
#is_readable(x)
#Error in file.info(x) : invalid filename argument
#Error in file.access(x, 4) : invalid 'names' argument
```
###7. Read the complete lyrics to “Little Bunny Foo Foo”. There’s a lot of duplication in this song. Extend the initial piping example to recreate the complete song, and use functions to reduce the duplication.
```{r}

```

#3. Functions are for humans and computers.
Create short but meaninful function names.
Be consistent with naming: snake_case or camelCase types.
Use common prefixes to indicate that functions are connected.
  input_select()
  input_checkbox()
  input_text()
Use str_ to find a function
Avoid overwriting existing functions. Bad:
  T<- FALSE
  c<- 10
Use comments, start writing comment with #.

### Exercises 1

####1.Read the source code for each of the following three functions, puzzle out what they do, and then brainstorm better names.
```{r}
f1<- function (string, prefix) {
  substr(string, 1, nchar(prefix))==prefix
}
f1(z, 1)
z

k<- NA
f2<- function(x) {
  if (length(x)<= 1) return(NULL)
    x[-length(x)]
}
f2(k)

h<- 5
f3<- function(x, y) {
  rep(y, length.out = length(x))
}
f3(z, h)
#repeats y x-times
```
####2. Take a function that you’ve written recently and spend 5 minutes brainstorming a better name for it and its arguments.
```{r}
find_prefix<- function (string, prefix) {
  substr(string, 1, nchar(prefix))==prefix
}
f1(z, 2)
z

k<- NA
f2<- function(x) {
  if (length(x)<= 1) return(NULL)
    x[-length(x)]
}
f2(z)

h<- 5
f3<- function(x, length) {
  rep(x, length.out = length(y))
}
f3(h, z)
```

####3. Compare and contrast rnorm() and MASS::mvrnorm(). How could you make them more consistent?
mvnorm() is a multivariate normal distribution (matrix), uses more than one vector.
rnorm() reates a sample from a normal distib. around mean and with st.dev.

####4.Make a case for why norm_r(), norm_d() etc would be better than rnorm(), dnorm(). Make a case for the opposite.
The common prefix (norm) at the begining of the name is better because autocomplete help that would give all "norm" functions.

#4. Conditional execution
If statement allowes to conditionally execute code:

if (condition){
  # code executed when condition is TRUE
} else {
  # code executed when condition is FALSE
}

Is each element of a vectore is named? Has_name will give true for value that has name:
```{r}
has_name<- function(x){
  nms<- names(x)  #names() gets or sets the names of an object
  if (is.null(nms)){
    rep(FALSE, length(x))  # vector of "FALSE" - no names 
  } else {
    !is.na(nms) & nms !=""
  }
}
x<- c("Yes", "No")
has_name(x)
z <- 1:3
names(z)
## assign just one name
names(z)[2] <- "b"
z
has_name(z)
```
### Conditions
The condition must evaluate to either TRUE or FALSE.
|| (or) will return the first TRUE.
&& (and) will return the first FALSE.
Don't use | or & in an if statement.
any() all() to colapce logical vector.
== is vectorised. Can have more then one output.
identical() returns a single TRUE or FALSE. Watch out for integers/doubles, and floating point numbers:
```{r}
identical(0L, 0)

x<- sqrt(2) ^2
x
x==2
x-2
```
### Multiple conditions
Chain multiple statements together:
r
if(this) {
  # do that
} else if {
  # do something else
} else {
  # do another
}

swith() allowes to evaluate selected code based on position, evaluates EXPR and accordingly chooses one of the further arguments (in ...). EXPR	an expression evaluating to a number or a character string.
```{r}
mult<- function(x, y, op){
  switch(op, 
         plus = x + y,
         minus = x - y,
         times = x * y,
         divide = x / y,
         stop("Unknown op!")
         )
}
x=4
y=8
mult(x, y, "plus")
```
cut() describes continuous variables.

### Code style
Both if and function should (almost) always be followed by squiggly brackets ({}), and the contents should be indented by two spaces. 
An opening curly brace should never go on its own line and should always be followed by a new line. A closing curly brace should always go on its own line, unless it’s followed by else. Always indent the code inside curly braces.
```{r}
if (y<0 && debug) {
  message("Y is negative")
}

if (y==0) {
  log(x)
} else {
  y^x
}
```
It’s ok to drop the curly braces if you have a very short if statement that can fit on one line:
```{r}
y<- 10
x<- if (y<20) "Too low" else "Too high"
x
```
### Exercises 2
####1. What’s the difference between if and ifelse()? Carefully read the help and construct three examples that illustrate the key differences.

  




