---
title: "Assingment_1"
author: "Nina Dyatchenko"
date: "October 5, 2018"
output: html_document
---

**1.** Work through this lesson on functions: https://swcarpentry.github.io/r-novice-inflammation/02-func-R/

**Defining Function**
```{r}
fahrenheit_to_kelvin <- function(temp_F) {
  temp_K <- ((temp_F - 32) * (5 / 9)) + 273.15
  return(temp_K)
}
# freezing point of water
fahrenheit_to_kelvin(32)

# boiling point of water
fahrenheit_to_kelvin(212)

kelvin_to_celsius <- function(temp_K) {
  temp_C <- temp_K - 273.15
  return(temp_C)
}
```
**Composing Functions**
```{r}
# absolute zero in Celsius
kelvin_to_celsius(0)

fahrenheit_to_celsius <- function(temp_F) {
  temp_K <- fahrenheit_to_kelvin(temp_F)
  temp_C <- kelvin_to_celsius(temp_K)
  return(temp_C)
}
```
**Nesting Functions** - “nesting” one function inside another.
```{r}
# freezing point of water in Celsius
fahrenheit_to_celsius(32.0)

# freezing point of water in Celsius
kelvin_to_celsius(fahrenheit_to_kelvin(32.0))

best_practice <- c("Write", "programs", "for", "people", "not", "computers")
asterisk <- "***"  # R interprets a variable with a single value as a vector
                   # with one element.

fence <- function(original, wrapper) {
  answer <- c(wrapper, original, wrapper)
  return(answer)
}
fence(best_practice, asterisk)

outside <- function(v) {
  first <- v[1]
   last <- v[length(v)]
   answer <- c(first, last)
   return(answer)
}
dry_principle <- c("Don't", "repeat", "yourself", "or", "others")
outside(dry_principle)
```
**The Call Stack** - Function calls are managed via the call stack. 

**Named Variables and Scope Variables** - Functions can accept arguments explicitly assigned to a variable name in in the function call functionName(variable = value), as well as arguments by order.
```{r}
input_1 <- 20
mySum <- function(input_1, input_2 = 10) {
  output <- input_1 + input_2
  return(output)
}
mySum(input_1 = 1, 3)

#mySum(3)
#mySum(input_2=3)
# Error: argument "input_1" is missing, with no default.
```
**Testing and Documenting** - start testing that those functions are working correctly.
```{r}
center <- function(data, desired) {
  new_data <- (data - mean(data)) + desired
  return(new_data)
}
z <- c(0, 0, 0, 0)
z
center(z, 3)
# works right

dat <- read.csv(file = "C:/Users/Nina/Documents/GitHub/BST650_Bootstrap/inflammation-01.csv", 
                header = FALSE)
centered <- center(dat[, 4], 0)
head(centered)
# original min
min(dat[, 4])
# original mean
mean(dat[, 4])
# original max
max(dat[, 4])
# centered min
min(centered)
# centered mean
mean(centered)
# centered max
max(centered)
# original standard deviation
sd(dat[, 4])
# centered standard deviation
sd(centered)
# difference in standard deviations before and after
sd(dat[, 4]) - sd(centered)

all.equal(sd(dat[, 4]), sd(centered))

center <- function(data, desired) {
  # return a new vector containing the original data centered around the
  # desired value.
  # Example: center(c(1, 2, 3), 0) => c(-1, 0, 1)
  new_data <- (data - mean(data)) + desired
  return(new_data)
}
```
**Functions to Create Graphs**
```{r}
analyze <- function(filename) {
  # Plots the average, min, and max inflammation over time.
  # Input is character string of a csv file.
  dat <- read.csv(file = filename, header = FALSE)
  avg_day_inflammation <- apply(dat, 2, mean)
  plot(avg_day_inflammation)
  max_day_inflammation <- apply(dat, 2, max)
  plot(max_day_inflammation)
  min_day_inflammation <- apply(dat, 2, min)
  plot(min_day_inflammation)
}
analyze("C:/Users/Nina/Documents/GitHub/BST650_Bootstrap/inflammation-01.csv")
```

**Rescaling** - takes a vector as input and returns a corresponding vector of values scaled to lie in the range 0 to 1.
```{r}
rescale <- function(v) {
  # Rescales a vector, v, to lie in the range 0 to 1.
  L <- min(v) # lowest value
  H <- max(v) # highers value
  result <- (v - L) / (H - L)
  return(result)
}

rescale(1:19)
```
**Defining Defaults** - we can pass the arguments to read.csv without naming them.
```{r}
dat <- read.csv("C:/Users/Nina/Documents/GitHub/BST650_Bootstrap/inflammation-01.csv", FALSE)

#re-define our center function
center <- function(data, desired = 0) {
  # return a new vector containing the original data centered around the
  # desired value (0 by default).
  # Example: center(c(1, 2, 3), 0) => c(-1, 0, 1)
  new_data <- (data - mean(data)) + desired
  return(new_data)
}
test_data <- c(0, 0, 0, 0)
center(test_data, 3)
more_data <- 5 + test_data
more_data
center(more_data)

display <- function(a = 1, b = 2, c = 3) {
  result <- c(a, b, c)
  names(result) <- c("a", "b", "c")  # This names each element of the vector
  return(result)
}

# no arguments
display()
# one argument
display(55)
# two arguments
display(55, 66)
# three arguments
display(55, 66, 77)
# only setting the value of c
display(c = 77)
```
**Matching Arguments** - R has three ways that arguments are supplied by you are matched to the formal arguments of the function definition.

read.csv(file, header = TRUE, sep = ",", quote = "\"",
        dec = ".", fill = TRUE, comment.char = "", ...)

**A Function with Default Argument Values** - Rewrite the rescale function so that it scales a vector to lie between 0 and 1 by default, but will allow the caller to specify lower and upper bounds if they want.
```{r}
rescale <- function(v, lower = 0, upper = 1) {
  # Rescales a vector, v, to lie in the range lower to upper.
  L <- min(v)
  H <- max(v)
  result <- (v - L) / (H - L) * (upper - lower) + lower
  return(result)
}
```
**2.** Create a function called `bootstrap()` that modifies the behaviour of the `sample()` function to perform a bootstrap sample on a given vector. Remember that bootstrap samples are the same **length** as the original sample, and remember that these samples are taken **with replacement** (*hint, hint*).

```{r}
bootstrap<- function(data) {
  sample1<- sample(data, size=length(data), replace = T) # sample with replacement
  return(sample1)
  }
```


bootstrap<- function(data, n) {
  sample1<- sample(data, size=length(data), replace = T) # sample with replacement
  #return(sample1)
  replic<- rep.int(sample1, n)
  return(replic)
}



**3.** Create the following vector: `grades = c(92, 80, 85, 95, 97, 78, 90, 86, 88, 66, 70, 82)`. Find the five-number summary, mean, and standard deviation of `grades`.

```{r}
grades = c(92, 80, 85, 95, 97, 78, 90, 86, 88, 66, 70, 82)
summary(grades)
sd(grades)
```

**4.** Call your function 10 times on `grades`. Store each bootstrapped sample as `boot1`, `boot2`, ..., `boot10`.
```{r}
boot1<- bootstrap(grades)
boot2<- bootstrap(grades)
boot3<- bootstrap(grades)
boot4<- bootstrap(grades)
boot5<- bootstrap(grades)
boot6<- bootstrap(grades)
boot7<- bootstrap(grades)
boot8<- bootstrap(grades)
boot9<- bootstrap(grades)
boot10<- bootstrap(grades)
```
**5.** Find the five-number summary, mean, and standard deviation of each bootstrap sample.
```{r}
summary(boot1)
sd(boot1)
summary(boot2)
sd(boot2)
summary(boot3)
sd(boot3)
summary(boot4)
sd(boot4)
summary(boot5)
sd(boot5)
summary(boot6)
sd(boot6)
summary(boot7)
sd(boot7)
summary(boot8)
sd(boot8)
summary(boot9)
sd(boot9)
summary(boot10)
sd(boot10)
```
**6.** Create a data frame of these summary statistics (10 rows and seven columns).
```{r}
BootsFrame <- data.frame(
  Bootstraps = c("boot1", "boot2", "boot3", "boot4", "boot5", 
                 "boot6", "boot7", "boot8", "boot9", "boot10"),
  MinBoot = c(min(boot1), min(boot2), min(boot3), min(boot4), min(boot5), 
              min(boot6), min(boot7), min(boot8), min(boot9), min(boot10)),
  Quart1 = c(IQR(boot1), IQR(boot2), IQR(boot3), IQR(boot4), IQR(boot5), 
             IQR(boot6), IQR(boot7), IQR(boot8), IQR(boot9), IQR(boot10)),
  MedianBoot = c(median(boot1), median(boot2), median(boot3), median(boot4), median(boot5), 
                 median(boot6), median(boot7), median(boot8), median(boot9), median(boot10)), 
  MeanBoot= c(mean(boot1), mean(boot2), mean(boot3), mean(boot4), mean(boot5), 
              mean(boot6), mean(boot7), mean(boot8), mean(boot9), mean(boot10)),
  MaxBoot= c(max(boot1), max(boot2), max(boot3), max(boot4), max(boot5), 
             max(boot6), max(boot7), max(boot8), max(boot9), max(boot10)),
  StDev = c(sd(boot1), sd(boot2), sd(boot3), sd(boot4), sd(boot5), 
            sd(boot6), sd(boot7), sd(boot8), sd(boot9), sd(boot10)),
  stringsAsFactors = FALSE)

head(BootsFrame)
```
**7.** Find the bootstrap estimate of each element of the five-number summary, mean, and standard deviation (look at the formula in your notes, then look at the `?colMeans` help file).
At 95% CI alpha = 0.05
```{r}
estimateInt <- function(data) {
  return(mean(data))
}
mean1<- estimateInt(BootsFrame$MinBoot)
mean1
```


```{r}
mean(BootsFrame$MinBoot)
mean(BootsFrame$Quart1)
mean(BootsFrame$MedianBoot)
mean(BootsFrame$MeanBoot)
mean(BootsFrame$MaxBoot)
mean(BootsFrame$StDev)
```