---
title: "Assingment_1"
author: "Nina Dyatchenko"
date: "October 5, 2018"
output: html_document
---

**1.** Work through this lesson on functions: https://swcarpentry.github.io/r-novice-inflammation/02-func-R/

**2.** Create a function called `bootstrap()` that modifies the behaviour of the `sample()` function to perform a bootstrap sample on a given vector. Remember that bootstrap samples are the same **length** as the original sample, and remember that these samples are taken **with replacement** (*hint, hint*).

```{r}
bootstrap<- function(data) {
  sample<- sample(data, replace = FALSE)
  return(sample)
}
```
**3.** Create the following vector: `grades = c(92, 80, 85, 95, 97, 78, 90, 86, 88, 66, 70, 82)`. Find the five-number summary, mean, and standard deviation of `grades`.

```{r}
grades = c(92, 80, 85, 95, 97, 78, 90, 86, 88, 66, 70, 82)
summary(grades)
sd(grades)
```

**4.** Call your function 10 times on `grades`. Store each bootstrapped sample as `boot1`, `boot2`, ..., `boot10`.
```{r}
boot1<- bootstrap(grades)
boot2<- bootstrap(grades)
boot3<- bootstrap(grades)
boot4<- bootstrap(grades)
boot5<- bootstrap(grades)
boot6<- bootstrap(grades)
boot7<- bootstrap(grades)
boot8<- bootstrap(grades)
boot9<- bootstrap(grades)
boot10<- bootstrap(grades)
```
**5.** Find the five-number summary, mean, and standard deviation of each bootstrap sample.
```{5}
summary(boot1)
sd(boot1)
summary(boot2)
sd(boot2)
summary(boot3)
sd(boot3)
summary(boot4)
sd(boot4)
summary(boot5)
sd(boot5)
summary(boot6)
sd(boot6)
summary(boot7)
sd(boot7)
summary(boot8)
sd(boot8)
summary(boot9)
sd(boot9)
summary(boot10)
sd(boot10)
```
**6.** Create a data frame of these summary statistics (10 rows and seven columns).
```{r}
BootsFrame <- data.frame(
  Bootstraps = c("boot1", "boot2", "boot3", "boot4", "boot5", "boot6", "boot7", "boot8", "boot9", "boot10"),
  MinBoot = c(min(boot1), min(boot2), min(boot3), min(boot4), min(boot5), 
              min(boot6), min(boot7), min(boot8), min(boot9), min(boot10)),
  Quart1 = c(IQR(boot1), IQR(boot2), IQR(boot3), IQR(boot4), IQR(boot5), 
             IQR(boot6), IQR(boot7), IQR(boot8), IQR(boot9), IQR(boot10)),
  MedianBoot = c(median(boot1), median(boot2), median(boot3), median(boot4), median(boot5), 
                 median(boot6), median(boot7), median(boot8), median(boot9), median(boot10)), 
  MeanBoot= c(mean(boot1), mean(boot2), mean(boot3), mean(boot4), mean(boot5), 
              mean(boot6), mean(boot7), mean(boot8), mean(boot9), mean(boot10)),
  
  StDev = c(sd(boot1), sd(boot2), sd(boot3), sd(boot4), sd(boot5), 
            sd(boot6), sd(boot7), sd(boot8), sd(boot9), sd(boot10))
  )
head(BootsFrame)
```
# stringsAsFactors = FALSE) # do not change strings to factors;
```{r}
BootsFrame2<- data.frame(
  Bootstrap1 = c(boot1, min(boot1), IQR(boot1), median(boot1), mean(boot1), sd(boot1)),
  Bootstrap2 = c(boot2, min(boot2), IQR(boot2), median(boot2), mean(boot2), sd(boot2)),
  Bootstrap3 = c(boot3, min(boot3), IQR(boot3), median(boot3), mean(boot3), sd(boot3)),
  Bootstrap4 = c(boot4, min(boot4), IQR(boot4), median(boot4), mean(boot4), sd(boot4))
)
head(BootsFrame2)
```
**7.** Find the bootstrap estimate of each element of the five-number summary, mean, and standard deviation (look at the formula in your notes, then look at the `?colMeans` help file).