---
title: "Assignment3_Bootstrap_10252018"
author: "Nina Dyatchenko"
date: "October 25, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read this chapter on functions and if/else statements in R:
http://r4ds.had.co.nz/functions.html
Create a markdown report where you execute the code from this chapter, and attempt the exercises after each section. Some of them will be more challenging than others, but I still want you to try to solve them.

Please upload this report to your GitHub by 11:59PM on Sunday, 28 October.

#1 Prerequisites#
Copies of the same code:
```{r}
# tibble builds a simple list/data_frame of a, b, c, and d with 10 values from a normal distribution:
df<- tibble::tibble(
  a=rnorm(10),
  b=rnorm(10),
  c=rnorm(10),
  d=rnorm(10)
)
df

df$a
df$b
df$c
df$d


# rescaling from 0 to 1:
df$a <- (df$a - min(df$a, na.rm = TRUE)) / 
  (max(df$a, na.rm = TRUE) - min(df$a, na.rm = TRUE))
df$b <- (df$b - min(df$b, na.rm = TRUE)) / 
  (max(df$b, na.rm = TRUE) - min(df$b, na.rm = TRUE)) 
df$c <- (df$c - min(df$c, na.rm = TRUE)) / 
  (max(df$c, na.rm = TRUE) - min(df$c, na.rm = TRUE))
df$d <- (df$d - min(df$d, na.rm = TRUE)) / 
  (max(df$d, na.rm = TRUE) - min(df$d, na.rm = TRUE))

df$a
df$b
df$c
df$d
```
Analysing the code: there is one input df$a (or df$b or df$c or df$d).
Rewriting code using a general variable name x:
```{r}
x<- df$a
(x-min(x, na.rm=TRUE))/ (max(x, na.rm=TRUE) - min(x, na.rm=TRUE))
```
Symplify:
```{r}
rng<- range(x, na.rm=TRUE)
xx<- (x-rng[1])/ (rng[2]-rng[1])
```
Combine all into a function:
```{r}
rescale01<- function(x){
  rng<-range(x, na.rm=T)
  (x-rng[1])/(rng[2]-rng[1])
}
rescale01(c(0, 5, 10))
```
Cheching function with different outputs:
```{r}
rescale01(c(8, 10, -9, 500))
rescale01(c(1, 9, NA, -9))
```
Applying the new function:
```{r}
df$a<- rescale01(df$a)
df$b<- rescale01(df$b)
df$c<- rescale01(df$c)
df$d<- rescale01(df$d)
df$a
```
Adjastign our function to unclude infinitine vlaues:
```{r}
x<- c(1:10, Inf)
rescale01(x)

rescale02<- function(x){
  rng<- range(x, na.rm=T, finite=T)
  (x-rng[1])/(rng[2]-rng[1])
}
rescale02(x)
```

#2 Practice#
###1. Why is TRUE not a parameter to rescale01()? What would happen if x contained a single missing value, and na.rm was FALSE?

